---
title: "Run EconML (allocation period 2: cross-sectional)"
author: "Shunkei Kakimoto"
output:
  html_document:
    number_sections: yes
    theme: flatly
    toc_float: yes
    toc: yes
    toc_depth: 3
geometry: margin=1in
---

```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir = "~/Dropbox/ResearchProject/HeterogeneousAllocation")

# library(here)
# opts_knit$set(root.dir = here())

knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE,
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)

# /*===== Basic Packages  =====*/
# /*---- Data Wrangling ----*/
library(data.table)
library(tidyverse)
library(DescTools)
library(maps)

# /*---- Visualization ----*/
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(viridis)
library(grid)
library(gridExtra)
library(GGally)

# /*---- Model Summary ----*/
library(stats)
library(modelsummary)
library(flextable)
library(officer)
library(officedown)
library(gt)
```		

# Objective
+ Forcus on the data from 2008-2012 (this period is associated with the allocation period 2)
  * use aggregated data (cross-sectional) by individual well


# Set up

```{r}
# setwd(here())
# /*===== R =====*/
source("./GitControlled/Codes/0_1_ls_packages.R")
source("./GitControlled/Codes/0_0_functions.R")

# /*===== python  =====*/
use_python("./myenv/bin/python")
use_virtualenv("./myenv/bin/activate_this.py")

source_python("./GitControlled/Codes/0_0_import_modules.py")
# source_python("./GitControlled/COdes/0_0_functions.py")

# /*===== Data (allocation period 2, 2008-2012 )=====*/
# --- panel data--- #
reg_data <- 
  readRDS("./Shared/Data/WaterAnalysis/comp_reg_dt.rds") %>%
  .[year %in% 2008:2012 & usage <= 40,]

# --- aggregated data (allocation period 2:2008:2012 by wells)--- #
reg_data_agg <- 
  data.table::copy(reg_data) %>%
  .[,`:=`(
    sum_usage = sum(usage),
    pr_in = sum(pr_in),
    sum_gdd = sum(gdd_in)
  ),by=wellid] %>%
  unique(., by="wellid")
```


# Preparation

+ Create training and testing dataset

+ include year FEs and individual FEs (from *panel_fe_dmlof.rmd*)
  * run `feols(usage ~ 1 | wellid + year, data = reg_data_agg)` and extract the coefficients of year FEs and individual FEs
    - those coefficients can be regarded as the unique impact associated with each individual and year. 


## Variables to be included
```{r}
# /*===== control variables =====*/
cov_ls <- c(
  # --- weather --- #
  "pr_in", "gdd_in","pet_in",
  # --- soil --- #
  "silttotal_r", "claytotal_r", "slope_r", "ksat_r", "awc_r"
  )

all_vars <- c(cov_ls, 'usage', 'treat2', 'tr', 'year')
```

# CF analysis

```{r}
# /*===== Training Dataset  =====*/
# --- dependent variable --- #
Y <- reg_data_agg[, usage]
# --- treatment indicator --- #
T <- reg_data_agg[, treat2]
# --- features --- #
# X <- reg_data_agg[, c(cov_ls, "ind_fe", "year_fe"), with=FALSE]
X <- reg_data_agg[, ..cov_ls]
# --- cluster  --- #
cl_var <- reg_data_agg[,tr] %>% as.factor()

# /*===== Run CF =====*/
forest_W <- boosted_regression_forest(X, T, tune.parameters = "all")
W_hat <- predict(forest_W)$predictions
forest_Y <- boosted_regression_forest(X, Y, tune.parameters = "all")
Y_hat <- predict(forest_Y)$predictions

res_cf <- causal_forest(
  X=X, Y=Y, W=T, 
  Y.hat = Y_hat, 
  W.hat = W_hat,
  clusters = cl_var,
  tune.parameters = "all",
)

# /*===== variable of importance  =====*/
var_imp <- 
  data.frame(
  # name = c(cov_ls, "year_fe", "ind_fe"),
  name = cov_ls,
  value = variable_importance(res_cf)[,1]
) %>%
arrange(desc(value))

gt(var_imp)
```

+ **Results**:
  * In aggregated data, soil variables: `slope_r`, `silttotal_r`, `awc_r` are the candidates for heterogeneity drivers

```{r}
# /*===== Visualization: TE estimates =====*/
gen_impact_viz(
  cf_res= res_cf,
  data_base=reg_data_agg,
  treat_var='treat2',
  var_ls= cov_ls,
  # var_ls= c(cov_ls, "year_fe", "ind_fe"),
  var_ls_int = cov_ls
  # var_ls= cov_ls
)
```

<br>


# DML-OrthoForest analysis

## Run DML-OrthoForest (`slope_r`, `silttotal_r`, `awc_r`)

+ Based on the reuslts from CF, I use `slope_r`, `silttotal_r`, `awc_r` as features that capture heterogeneity

### Training Data

```{r}
het_vars_v1 <- c("slope_r", "silttotal_r", "awc_r")

# --- dependent variable --- #
Y <- reg_data_agg[, usage] %>% as.array()
# --- treatment indicator --- #
T <- reg_data_agg[, treat2] %>% as.array()
# --- heterogeneous impact dirivers --- #
X <- reg_data_agg[, ..het_vars_v1] %>% as.matrix()
# --- controls --- #
# W <- reg_data_agg[,c(cov_ls, "year_fe", "ind_fe"), with=FALSE] %>%
#   as.matrix()
W <- reg_data_agg[,c(cov_ls), with=FALSE] %>%
  as.matrix()
```

### Testing Data

```{r}
X_test_comp <- 
  lapply(het_vars_v1, function(x) gen_pred_data(reg_data_agg, het_vars_v1, x)) %>%
  bind_rows()

X_test <- 
  X_test_comp[,!"target_var"] %>%
  as.matrix()
```

```{python}
# repl_python()
lambda_reg=0.33

est = DMLOrthoForest(
    n_trees=1000,
    min_leaf_size=20,
    max_depth=50,
    subsample_ratio=0.7,
    model_T=Lasso(alpha=lambda_reg),
    model_Y=Lasso(alpha=lambda_reg),
    model_T_final=WeightedLasso(alpha=lambda_reg),
    model_Y_final=WeightedLasso(alpha=lambda_reg),
    global_residualization=False
    )

est.fit(r.Y, r.T, X=r.X, W=r.W)

treatment_effects = est.effect(r.X_test)

te_lower, te_upper = est.effect_interval(r.X_test)
```

### Visualization

```{r}
res_dml_orf_v1 <- 
  data.table(
    te_pred = py$treatment_effects,
    te_lower = py$te_lower,
    te_upper = py$te_upper
  ) %>%
  cbind(X_test_comp, .)

gen_econml_vis(res_econml_dt=res_dml_orf_v1, het_vars =het_vars_v1)
```

<br>

<br>


## Run DML-OrthoForest (`pr_in`, `gdd_in`, `pet_in`)

+ What if I use `pr_in`, `gdd_in`, and `pet_in` as features that capture heterogeneity, like the same way we did in the case of panel dataset.

### Training Data

```{r}
het_vars_v2 <- c("pr_in", "gdd_in", "pet_in")

# --- dependent variable --- #
Y <- reg_data_agg[, usage] %>% as.array()
# --- treatment indicator --- #
T <- reg_data_agg[, treat2] %>% as.array()
# --- heterogeneous impact dirivers --- #
X <- reg_data_agg[, ..het_vars_v2] %>% as.matrix()
# --- controls --- #
# W <- reg_data_agg[,c(cov_ls, "year_fe", "ind_fe"), with=FALSE] %>%
#   as.matrix()
W <- reg_data_agg[,c(cov_ls), with=FALSE] %>%
  as.matrix()
```

### Testing Data

```{r}
X_test_comp <- 
  lapply(het_vars_v2, function(x) gen_pred_data(reg_data_agg, het_vars_v2, x)) %>%
  bind_rows()

X_test <- 
  X_test_comp[,!"target_var"] %>%
  as.matrix()

head(X_test)
```

```{python}
# repl_python()
lambda_reg=0.33

est = DMLOrthoForest(
    n_trees=1000,
    min_leaf_size=20,
    max_depth=50,
    subsample_ratio=0.7,
    model_T=Lasso(alpha=lambda_reg),
    model_Y=Lasso(alpha=lambda_reg),
    model_T_final=WeightedLasso(alpha=lambda_reg),
    model_Y_final=WeightedLasso(alpha=lambda_reg),
    global_residualization=False
    )

est.fit(r.Y, r.T, X=r.X, W=r.W)

treatment_effects = est.effect(r.X_test)

te_lower, te_upper = est.effect_interval(r.X_test)
```

### Visualization

```{r}
res_dml_orf_v2 <- 
  data.table(
    te_pred = py$treatment_effects,
    te_lower = py$te_lower,
    te_upper = py$te_upper
  ) %>%
  cbind(X_test_comp, .)

gen_econml_vis(res_econml_dt=res_dml_orf_v2, het_vars =het_vars_v2)
```