---
title: "Orthogonal Random Forest and Causal Forest: Use Cases and Examples"
author: "Shunkei Kakimoto"
date: ""
output: html_document
---


```{r setup, include=FALSE}
library(knitr)
library(here)
library(reticulate)
library(tidyverse) # for data wrangling and visualization
library(recipes)   # for data preprocessing
library(data.table)

opts_knit$set(root.dir = here())

opts_chunk$set(
  fig.align = "center", 
  fig.retina = 5,
  warning = FALSE, 
  message = FALSE,
  cache = FALSE, # <-- T
  cache.lazy = FALSE,
  echo = TRUE
  )
```

## Question
+ How to open R project from terminus?


## I need to set the path manually instead using of here()

+ **Problem**: The path to the project `here()` should specify does not correct
  * It should be: `/Users/shunkeikakimoto/Dropbox/ResearchProject/HeterogeneousAllocation`
  * but, whenever I use `here()` on Rmarkdown, the path is set `/Users/shunkeikakimoto/Dropbox/ResearchProject/HeterogeneousAllocation/GitControlled/GW_het_allocation_impact`
  * I do not understand why. Maybe because of git?


```{r}
here()
use_python("/Users/shunkeikakimoto/Dropbox/ResearchProject/HeterogeneousAllocation/myenv/bin/python")
use_virtualenv("/Users/shunkeikakimoto/Dropbox/ResearchProject/HeterogeneousAllocation/myenv/bin/activate_this.py")

py_config()
```

# Setup

```{python}
import econml

# Main imports
from econml.orf import DMLOrthoForest, DROrthoForest
from econml.dml import CausalForestDML
from econml.sklearn_extensions.linear_model import WeightedLassoCVWrapper, WeightedLasso, WeightedLassoCV

# Helper imports
import numpy as np
from itertools import product
from sklearn.linear_model import Lasso, LassoCV, LogisticRegression, LogisticRegressionCV
import matplotlib.pyplot as plt

# %matplotlib inline #this is not correct syntax for Python (?)
```

# Example Usage with Continuous Treatment Synthetic Data

```{python}
# Treatment effect function
def exp_te(x):
    return np.exp(2*x[0])
```

```{python}
# DGP constants
np.random.seed(123)
n = 1000
n_w = 30
support_size = 5
n_x = 1
# Outcome support
support_Y = np.random.choice(range(n_w), size=support_size, replace=False)
coefs_Y = np.random.uniform(0, 1, size=support_size)
epsilon_sample = lambda n: np.random.uniform(-1, 1, size=n)
# Treatment support 
support_T = support_Y
coefs_T = np.random.uniform(0, 1, size=support_size)
eta_sample = lambda n: np.random.uniform(-1, 1, size=n) 

# Generate controls, covariates, treatments and outcomes
W = np.random.normal(0, 1, size=(n, n_w))
X = np.random.uniform(0, 1, size=(n, n_x))
# Heterogeneous treatment effects
TE = np.array([exp_te(x_i) for x_i in X])
T = np.dot(W[:, support_T], coefs_T) + eta_sample(n)
Y = TE * T + np.dot(W[:, support_Y], coefs_Y) + epsilon_sample(n)

# ORF parameters and test data
subsample_ratio = 0.3
lambda_reg = np.sqrt(np.log(n_w) / (10 * subsample_ratio * n))
X_test = np.array(list(product(np.arange(0, 1, 0.01), repeat=n_x)))
```

## Train Estimator

```{python}
est = DMLOrthoForest(
    n_trees=1000, min_leaf_size=5,
    max_depth=50, subsample_ratio=subsample_ratio,
    model_T=Lasso(alpha=lambda_reg),
    model_Y=Lasso(alpha=lambda_reg),
    model_T_final=WeightedLasso(alpha=lambda_reg),
    model_Y_final=WeightedLasso(alpha=lambda_reg),
    global_residualization=False,
    random_state=123)
```

```{python}
est.fit(Y, T, X=X, W=W, inference="blb")
```

```{python}
# Calculate treatment effects
treatment_effects = est.effect(X_test)
```

```{python}
# Calculate default (95%) confidence intervals for the test data
te_lower, te_upper = est.effect_interval(X_test)
```

```{python}
res = est.effect_inference(X_test)
```

```{python}
res.summary_frame().head()
```

```{python}
res.population_summary()
```












