---
title: "gridMET and GiSSURGO"
author: "Shunkei Kakimoto"
output:
  html_document:
    number_sections: yes
    theme: cerulean
    toc_float: yes
    toc: yes
    toc_depth: 3
geometry: margin=1in
---

```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir = "~/Dropbox/ResearchProject/HeterogeneousAllocation")

# library(here)
# opts_knit$set(root.dir = here())

knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE,
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)

# /*===== Basic Packages  =====*/
# /*---- Data Wrangling ----*/
library(data.table)
library(tidyverse)
library(DescTools)
library(maps)

# /*---- Visualization ----*/
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(viridis)
library(grid)
library(gridExtra)
library(GGally)

# /*---- Model Summary ----*/
library(stats)
library(modelsummary)
library(flextable)
library(officer)
library(officedown)
```

# Object
+ Summarize what I did for data downloading 


# gridMET

+ Target variables:
	*  "pr":  precipitation (mm)
	*  "tmmn":  Minimum Near-Surface Air Temperature (Kelvin)
	*  "tmmx":  Maximum Near-Surface Air Temperature (Kelvin)
	*  "pet" : Reference grass evaportranspiration (mm)

+ Using well-level data (point data), extract values from gridMET raster data (2007-2015)
  * extract only in season daily data (i.e., from 4/1 to 9/30)
+ change those units
  * pr: mm to inch
  * tmmn: K to C
  * tmmx: K to C
  * pet: mm to inch
+ calculate daily GDD from tmmn and tmmx
+ summarize those variables by year and well id

# SSURGO

## Description about target variables

+ Target variables (reference website: here[https://sdmdataaccess.sc.egov.usda.gov/documents/TablesAndColumnsReport.pdf])
	* **sandtotal_r**: 
		- %
		- Mineral particles 0.05mm to 2.0mm in equivalent diameter as a weight percentage of the less than 2 mm fraction
	* **silttotal_r**: 
		- %
		- Mineral particles 0.002 to 0.05mm in equivalent diameter as a weight percentage of the less than 2.0mm fraction
	* **claytotal_r**: 
		- %
		- Mineral particles less than 0.002mm in equivalent diameter as a weight percentage of the less than 2.0mm fraction
	* **ksat_r**: 
		- um/s
		- The amount of water that would move vertically through a unit area of saturated soil in unit time under unit hydraulic gradient.
	* **awc_r**: 
		- cm/cm
		- The amount of water that an increment of soil depth, inclusive of fragments, can store that is available to plants. AWC is expressed as a volume fraction, and is commonly estimated as the difference between the water contents at 1/10 or 1/3 bar (field capacity) and 15 bars (permanent wilting point) tension and adjusted for salinity, and fragments.
	* **slope_r**
		- %
		- The difference in elevation between two points, expressed as a percentage of the distance between those points. (SSM) 

+ There are many similar variables depends on the particle size
	* Ex) in the sand case
		- sandtotal_ : Mineral particles 0.05mm to 2.0mm in equivalent diameter
		- sandvc_ : Mineral particles 1.0mm to 2.0mm in equivalent diameter
		- sandco_ : Mineral particles 0.5mm to 1.0mm in equivalent diameter
		- sandmed_: Mineral particles 0.25mm to 0.5mm in equivalent
		- sandfine_ : Mineral particles 0.10 to 0.25mm in equivalent diameter
		- sandvf_ : Mineral particles 0.05 to 0.10mm in equivalent diameter 


## Process
+ make buffer (400 m radius circles around well, which covers about 50 ha of land) for each well 

```{r}
source("./GitControlled/Codes/0_1_ls_packages.R")
source("./GitControlled/Codes/0_0_functions.R")
# /*===== point data for well location =====*/
data_w_LR_TB <- readRDS("./Shared/Data/WaterAnalysis/data_w_LR_TB.rds")

well_sf <- data_w_LR_TB %>%
  unique(.,by="wellid") %>%
  .[,.(wellid, longdd, latdd)] %>%
  # --- the geographic coordinate in the well data is NAD83 (espg=4269)--- #
  st_as_sf(., coords = c("longdd","latdd"), crs = 4269)


# /*===== make buffer around each well  =====*/
well_buffer_sf <- well_sf %>%
  #--- project to WGS UTM 14 (Cartesian 2D CS covering NE)---#
  st_transform(32614) %>%
  # --- make buffers--- #
  # 400 m radius circles around well, which covers about 50 ha of land
  st_buffer(., dist = 400)
 
ggplot()+
  geom_sf(data=well_sf, size=0.5) +
  geom_sf(data=well_buffer_sf, color="red", fill=NA)


well_buffer_sp <- as(well_buffer_sf, "Spatial")
```

+ Then, apply `get_ssurgo_props()` for each well buffer. 

```{r}
get_ssurgo_props <- function(field, vars, summarize = FALSE) {
  # field=unique_well_sp; vars = c("sandtotal_r", "claytotal_r")
  # Get SSURGO mukeys for polygon intersection
  ssurgo_geom <-
    SDA_spatialQuery(
      geom = field,
      what = "geom",
      db = "SSURGO",
      geomIntersection = TRUE
    ) %>%
    st_as_sf()
    mutate(
      area = as.numeric(st_area(.)),
      area_weight = area / sum(area)
    )

  # Get soil properties for each mukey
  mukeydata <-
    get_SDA_property(
      property = vars,
      method = "Weighted Average",
      mukeys = ssurgo_geom$mukey,
      top_depth = 0,
      bottom_depth = 150
    )

  ssurgo_data <- left_join(ssurgo_geom, mukeydata, by = "mukey")
  
  if (summarize == TRUE) {
    ssurgo_data_sum <-
      ssurgo_data %>%
      data.table() %>%
      .[,
        lapply(.SD, weighted.mean, w = area_weight),
        .SDcols = vars
      ]
    return(ssurgo_data_sum)
  } else {
    return(ssurgo_data)
  }
}
```

### Example: SSURGO polygon data for an example field

```{r}
library(soilDB)
library(aqp)
library(sp)

ex_well_bf <- well_buffer_sf[5,]
ex_well_bf_sp <- as(ex_well_bf, "Spatial")

ssurgo_geom <-
    SDA_spatialQuery(
      geom = ex_well_bf_sp,
      what = "geom",
      db = "SSURGO",
      geomIntersection = TRUE
    ) %>%
    st_as_sf()%>%
    dplyr::mutate(
      area = as.numeric(st_area(.)),
      area_weight = area / sum(area)
    )

# /*===== visualization =====*/
ggplot()+
  geom_sf(data=ssurgo_geom, aes(fill=factor(mukey)), color="blue", alpha=0.5)+
  geom_sf(data= well_sf[5,], fill=NA)
```



