---
title: "Prepare for CF Regression Analysis"
author: "Shunkei Kakimoto"
output:
  html_document:
    number_sections: yes
    theme: flatly
    toc_float: yes
    toc: yes
    toc_depth: 3
geometry: margin=1in
---

```{r setup, include=FALSE}
library(knitr)
library(here)

here::i_am("GitControlled/Codes/2_0_prepare_cf_analysis.rmd")

# opts_knit$set(root.dir = "")
# opts_knit$set(root.dir = here())

knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE,
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)

# /*===== Basic Packages  =====*/
# /*---- Data Wrangling ----*/
library(data.table)
library(tidyverse)
library(DescTools)
library(maps)

# /*---- Visualization ----*/
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(viridis)
library(grid)
library(gridExtra)
library(GGally)

# /*---- Model Summary ----*/
library(stats)
library(modelsummary)
library(flextable)
library(officer)
library(officedown)
library(gt)
```

```{r, echo=F}
map_theme <-
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```
  

# Objectives
+ remove data on landowners who own multiple farmlands across inside and outside of 5-miles or 10-miles buffers of LR side. 
+ For LR data, convert yearly well-level data to **yearly owner-level data**
  * Consider clustering variable: `cntyname`
  * Take weighted average ($sum(volaf*12)/sum(acres)$)

+ Final output:
  * `reg_data_5mi`
  * `reg_data_10mi`

## Data

```{r, echo=F}
# === setup === #
library(here)
source(here("GitControlled/Codes/0_1_ls_packages.R"))
source(here("GitControlled/Codes/0_0_functions.R"))
```

```{r}
#/*--------------------------------*/
#' ## Data
#/*--------------------------------*/
# === NRD boundary === #
nrd_boud <- 
 here("Shared/Data/WaterAnalysis/NRD_bd/BND_NaturalResourceDistricts_DNR.shp") %>%
 st_read() %>%
 filter(NRD_Name %in% c("Lower Republican", "Tri-Basin")) %>%
 st_transform(4269)


# === All well data === #
ir_data <- 
  here("Shared/Data/WaterAnalysis/ir_data_nw.rds") %>%
  readRDS() %>%
  data.table() %>%
  .[source %in% c('Meter','METER','metered') & nrdname %in% c("Lower Republican", "Tri-Basin")] %>%
  .[,owner_name := paste0(firstname, "_", lastname)] %>%
  .[,nrd_owner_name := paste0(nrdname, " ", owner_name) ]

# === Regression Data (period: 2008-2015)  === #
w_analysis_dt <- 
  here("Shared/Data/WaterAnalysis/w_analysis_dt.rds") %>%
  readRDS() %>%
  .[,nrd_owner_name := paste0(nrdname, " ", owner_name)] %>%
  .[year %in% 2008:2015 & usage <= 45]

# === Regression Data (period: 2008-2012) === #
reg_data <- 
  w_analysis_dt %>%
  .[year %in% 2008:2012]
```


# Identify landowners whose farmland located in both inside and outside of the 5 mile or 10 mile buffer

```{r, echo=F, eval=F}
# Don't need to run
#/*--------------------------------*/
#' ## Num of owners by NRD (After distinguished owners)
#/*--------------------------------*/

# === 5 miles criterion === #
# total number of farmers in the data: 1386
# TB: 444
# LR: 386
unique(reg_data[in_5mi==1,]$nrd_owner_name) %>% length()

reg_data[in_5mi==1,] %>%
  unique(., by = "nrd_owner_name") %>%
  .[, .N, by = nrdname]

# === 10 miles criterion === #
# total number of farmers in the data: 1386
# TB: 693
# LR: 693
reg_data %>%
  unique(., by = "nrd_owner_name") %>%
  .[, .N, by = nrdname]
```


```{r}
# === A list of owners who owns farmland outside of the 5 and 10 mi buffer in LR side === #
ls_owners_out5mi_LR <- 
  ir_data %>%
  .[nrdname=="Lower Republican" & in_5mi==0, nrd_owner_name] %>%
  unique()

ls_owners_out10mi_LR <- 
  ir_data %>%
  .[nrdname=="Lower Republican" & in_10mi==0, nrd_owner_name] %>%
  unique()

# === Create "both_InOut_5mi" and "both_InOut_10mi" index === #
# Ex) both_InOut_5mi==1, if an landowner has farmland outside of the 5 miles in LR side
reg_data <- 
  reg_data %>% 
  .[, `:=`(
    both_InOut_5mi_LR = ifelse(nrd_owner_name %in% ls_owners_out5mi_LR, 1, 0),
    both_InOut_10mi_LR = ifelse(nrd_owner_name %in% ls_owners_out10mi_LR, 1, 0)
    )]
```

```{r, echo=F, eval=F}
# Don't need to run
# === Check === #
reg_data_sf <-  st_as_sf(reg_data, coords = c("longdd","latdd"), crs = 4269)

ggplot() +
  geom_sf(data=nrd_boud) +
  geom_sf(data = filter(reg_data_sf, nrdname == "Lower Republican"), aes(color=factor(both_InOut_5mi_LR)), size=0.5)

ggplot() +
  geom_sf(data=nrd_boud) +
  geom_sf(data = filter(reg_data_sf, nrdname == "Lower Republican"), aes(color=factor(both_InOut_10mi_LR)), size=0.5)
```



```{r, echo=F, eval=F}
# Don't need to run
#/*--------------------------------*/
#' ## Num of owners by NRD (After distinguished owners)
#/*--------------------------------*/
# === 5 miles criterion === #
# total number of farmers in the data: 748
# TB: 444
# LR: 304
unique(reg_data[in_5mi==1&both_InOut_5mi_LR==0,]$nrd_owner_name) %>% length()

reg_data[in_5mi==1&both_InOut_5mi_LR==0,] %>%
  unique(., by = "nrd_owner_name") %>%
  .[, .N, by = nrdname]

# === 10 miles criterion === #
# total number of farmers in the data: 1386
# TB: 693
# LR: 638
reg_data[both_InOut_10mi_LR==0,] %>%
  unique(., by = "nrd_owner_name") %>%
  .[, .N, by = nrdname]
```


```{r}
# === 5 miles buffers === #
reg_data[in_5mi==1] %>%
  unique(., by="nrd_owner_name") %>%
  .[, .N, by=.(nrdname, both_InOut_5mi_LR) ] %>%
  .[order(nrdname)] %>%
  print()

# === 10 miles buffers === #
reg_data[in_10mi==1] %>%
  unique(., by="nrd_owner_name") %>%
  .[, .N, by=.(nrdname, both_InOut_10mi_LR) ] %>%
  .[order(nrdname)] %>%
  print()
```


+ 5 miles buffer criteria: 
  * 82 owners in LR also have farmlands outside of the buffer
+ 10 miles buffer criteria: 
  * 55 owners in LR also have farmlands outside of the buffer


# Create Raw Regression Data for 5 miles and 10 miles criterion, respectively

## Regression data with 5 miles criterion

### Problem

+ **Which variable should be used for clustering?**
  + I used to use `tr` (combinations of "township" and "range" index) for clustering. 
+ However, since some farmers have multiple wells across `tr`, so `tr` cannot be used.
  * If a farmer has farmland across several "range", the value of `tr` is not one, when we aggregated LR data by owner and year. 

+ We need some new geographic segmentation index which covers larger area.
  * Alternatives:
    - **County**

<br>

+ Check weather all the farmlands owned by a single owner in LR located in the same county.
  * For those who have multiple wells across several counties, find in which county their large portion of farmlands were located based on the total acres by county.
  * Create `cntyname_fix` 


### Cluster variable: `cntyname` for `reg_data_LR_5mi` data


```{r}
# - Data on TB - #
reg_data_TB_5mi <- 
  reg_data[in_5mi==1 & nrdname=="Tri-Basin",]

# - Data on LR - #
reg_data_LR_5mi <- 
  reg_data[in_5mi==1 & both_InOut_5mi_LR==0 & nrdname=="Lower Republican",]

reg_data_5mi_raw <- 
  bind_rows(reg_data_TB_5mi, reg_data_LR_5mi)
```


```{r}
# === A list of landowners whose farmlands are located in several counties  === #
ls_cnty_5mi <- 
  reg_data_5mi_raw %>%
  distinct(nrd_owner_name, cntyname) %>%
  .[, index := rep(1, nrow(.)),] %>%
  dcast(.,nrd_owner_name ~ cntyname, value.var = "index") %>%
  replace(is.na(.), 0) %>%
  .[, total := rowSums(.SD), by = nrd_owner_name] %>%
  .[total>1, ]
```

Example maps for those farmlands are shown in the below. 

```{r, echo=F}
ne_cnty_sf <-  tigris::counties("Nebraska", cb = TRUE, resolution="20m", progress_bar = FALSE) %>%
  dplyr::select(COUNTYFP, NAME) %>%
  filter(NAME %in% str_to_sentence(unique(reg_data$cntyname)))%>%
  st_transform(4269)

ex_cnty_5_sf <-
  reg_data_5mi_raw %>%
  .[nrd_owner_name %in% ls_cnty_5mi[,nrd_owner_name][1:6],] %>%
  distinct(nrd_owner_name, longdd, latdd, .keep_all = TRUE) %>%
  st_as_sf(., coords = c("longdd","latdd"), crs = 4269)

ggplot()+
  geom_sf(data=ne_cnty_sf, aes(fill=NAME), alpha=0.6) +
  geom_sf(data=nrd_boud, color="blue", fill=NA) +  
  geom_sf(data=ex_cnty_5_sf, size=1)+
  facet_wrap(~nrd_owner_name, ncol=3) +
  map_theme
```

<br>

+ Create `cntyname_fix` column which contains modified `cntyname`.
+ In the below, I decided in which county the farmers should be belong to based on the total acres of the farmlands by county. 

<br>

```{r}
which_cnty_5 <-
  reg_data_5mi_raw %>%
  .[nrd_owner_name %in% ls_cnty_5mi[, nrd_owner_name],] %>%
  distinct(nrd_owner_name, longdd, latdd, .keep_all = TRUE) %>%
  .[,.(sum_acres = sum(acres)), by = .(nrd_owner_name, cntyname)] %>%
  .[,.SD[sum_acres == max(sum_acres), ], by = nrd_owner_name]

which_cnty_5[, .N, by = cntyname]

Phelps <- which_cnty_5[cntyname=="Phelps", nrd_owner_name]
Kearney <- which_cnty_5[cntyname=="Kearney", nrd_owner_name]
Gosper <- which_cnty_5[cntyname=="Gosper", nrd_owner_name]
Harlan <- which_cnty_5[cntyname=="Harlan", nrd_owner_name]
Furnas <- which_cnty_5[cntyname=="Furnas", nrd_owner_name]

reg_data_5mi_raw <- 
  reg_data_5mi_raw %>%
  .[,cntyname_fix := case_when(
    nrd_owner_name %in% Phelps ~ "Phelps",
    nrd_owner_name %in% Kearney ~ "Kearney",
    nrd_owner_name %in% Gosper ~ "Gosper",
    nrd_owner_name %in% Harlan ~ "Harlan",
    nrd_owner_name %in% Furnas ~ "Furnas",
    TRUE ~ cntyname
  )]
```

```{r, echo=F, eval=F}
# Don't need to run
# === Check === #
cnty_5_check <- 
  reg_data_5mi_raw %>%
  distinct(nrd_owner_name, cntyname_fix) %>%
  .[, index := rep(1, nrow(.)),] %>%
  dcast(.,nrd_owner_name ~ cntyname_fix, value.var = "index") %>%
  replace(is.na(.), 0) %>%
  .[, total := rowSums(.SD), by = nrd_owner_name]

cnty_5_check[total>1, ]
```


```{r}
# === save the modified data  === #
saveRDS(reg_data_5mi_raw, here("Shared/Data/WaterAnalysis/reg_data_5mi_raw.rds"))
```


## Regression data with 10 miles criterion

### Cluster variable: `cntyname` for `reg_data_LR_10mi` data

+ Do the same things: 

```{r}
# - Data on TB - #
reg_data_TB_10mi <- 
  reg_data[nrdname=="Tri-Basin",]

# - Data on LR - #
reg_data_LR_10mi <- 
  reg_data[both_InOut_10mi_LR==0 & nrdname=="Lower Republican",]

reg_data_10mi_raw <- 
  bind_rows(reg_data_TB_10mi, reg_data_LR_10mi)
```


```{r}
cnty_10 <- 
  reg_data_10mi_raw %>%
  distinct(nrd_owner_name, cntyname) %>%
  .[, index := rep(1, nrow(.)),] %>%
  dcast(.,nrd_owner_name ~ cntyname, value.var = "index") %>%
  replace(is.na(.), 0) %>%
  .[, total := rowSums(.SD), by = nrd_owner_name]

# county_cl[total>1, nrd_owner_name]
cnty_10[total>1, ]
```

The map of those farmlands are shown in the below. 

```{r, echo=F}
# In the below,  based on the total acres of the farmlands by county, judge in which county the farmers should be belong to. 

which_cnty_10 <-
  reg_data_10mi_raw %>%
  .[nrd_owner_name %in% cnty_10[total>1, nrd_owner_name],] %>%
  distinct(nrd_owner_name, longdd, latdd, .keep_all = TRUE) %>%
  .[,.(sum_acres = sum(acres)), by = .(nrd_owner_name, cntyname)] %>%
  .[,.SD[sum_acres == max(sum_acres), ], by = nrd_owner_name]

# which_cnty_10[, .N, by = cntyname]

Phelps <- which_cnty_10[cntyname=="Phelps", nrd_owner_name]
Kearney <- which_cnty_10[cntyname=="Kearney", nrd_owner_name]
Gosper <- which_cnty_10[cntyname=="Gosper", nrd_owner_name]
Harlan <- which_cnty_10[cntyname=="Harlan", nrd_owner_name]
Furnas <- which_cnty_10[cntyname=="Furnas", nrd_owner_name]
Franklin <- which_cnty_10[cntyname=="Franklin", nrd_owner_name]

reg_data_10mi_raw <- 
  reg_data_10mi_raw %>%
  .[,cntyname_fix := case_when(
    nrd_owner_name %in% Phelps ~ "Phelps",
    nrd_owner_name %in% Kearney ~ "Kearney",
    nrd_owner_name %in% Gosper ~ "Gosper",
    nrd_owner_name %in% Harlan ~ "Harlan",
    nrd_owner_name %in% Furnas ~ "Furnas",
    nrd_owner_name %in% Franklin ~ "Franklin",
    TRUE ~ cntyname
  )]
```

```{r}
# === Save the modified data === #
saveRDS(reg_data_10mi_raw, here("Shared/Data/WaterAnalysis/reg_data_10mi_raw.rds"))
```


```{r}
# === Check === #
cnty_10_check <- 
  reg_data_10mi_raw %>%
  distinct(nrd_owner_name, cntyname_fix) %>%
  .[, index := rep(1, nrow(.)),] %>%
  dcast(.,nrd_owner_name ~ cntyname_fix, value.var = "index") %>%
  replace(is.na(.), 0) %>%
  .[, total := rowSums(.SD), by = nrd_owner_name]

# county_cl[total>1, nrd_owner_name]
cnty_10_check[total>1, ]
```


















