---
title: "CF analysis"
author: "Shunkei Kakimoto"
output:
  html_document:
    number_sections: yes
    theme: flatly
    toc_float: yes
    toc: yes
    toc_depth: 3
geometry: margin=1in
---

```{r setup, include=FALSE}
library(knitr)
library(here)

here::i_am("GitControlled/Codes/2_1_2_CF_10miles.rmd")

# opts_knit$set(root.dir = "")
# opts_knit$set(root.dir = here())

knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE,
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)

# /*===== Basic Packages  =====*/
# /*---- Data Wrangling ----*/
library(data.table)
library(tidyverse)
library(DescTools)
library(maps)

# /*---- Visualization ----*/
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(viridis)
library(grid)
library(gridExtra)
library(GGally)

# /*---- Model Summary ----*/
library(stats)
library(modelsummary)
library(flextable)
library(officer)
library(officedown)
library(gt)

```

```{r, echo=F}
map_theme <-
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

```{r, echo=F}
# === setup === #
library(here)
source(here("GitControlled/Codes/0_1_ls_packages.R"))
source(here("GitControlled/Codes/0_0_functions.R"))
```

# Objectives
+ Using well data in the 10 miles buffer, do CF analysis with:
  * Panel data
    - For LR data, owner-level
    - For TB data, well-level
  * Cross-sectional data 
    - For LR data, owner-level
    - For TB data, well-level

# Panel data

## Data in the 10 miles buffer

```{r}
reg_data_10mi_raw <- 
	here("Shared/Data/WaterAnalysis/reg_data_10mi_raw.rds") %>%
	readRDS()

# - Data on TB - #
TB_10mi <- reg_data_10mi_raw[nrdname=="Tri-Basin",]
# - Data on LR - #
LR_10mi <- reg_data_10mi_raw[nrdname=="Lower Republican",]
```

### LR Data

+ The data is aggregated by `nrd_owner_name` and `year`. 
+ In aggregating the data, the variable should be taken by mean weighted by `acres`.

```{r}
LR_10mi_y_owner <-
  LR_10mi %>%
  .[,.(
    usage = weighted.mean(usage, acres/sum(acres)),
    treat2 = mean(treat2),
    total_acres = sum(acres),
    # --- soil --- #
    silttotal_r = weighted.mean(silttotal_r, acres/sum(acres)),
    claytotal_r = weighted.mean(claytotal_r, acres/sum(acres)),
    slope_r = weighted.mean(slope_r, acres/sum(acres)),
    ksat_r = weighted.mean(ksat_r, acres/sum(acres)),
    awc_r = weighted.mean(awc_r, acres/sum(acres)),
    # --- weather --- #    
    pr_in = weighted.mean(pr_in, acres/sum(acres)),
    pet_in = weighted.mean(pet_in, acres/sum(acres)),
    gdd_in = weighted.mean(gdd_in, acres/sum(acres)),
    # --- tr --- #
    cntyname_fix = unique(cntyname_fix)
  ), by = .(nrd_owner_name, year)] %>%
  .[,county_year := paste0(cntyname_fix, "_", year)]

```

### TB Data

+ For TB data, keep using yearly well-level data.

```{r}
se_vars <- names(LR_10mi_y_owner) %>% .[.!="acres"]

TB_10mi_y_well <-
  TB_10mi %>%
  .[,county_year := paste0(cntyname, "_", year)] %>%
  .[, ..se_vars]
```

### Regression Data

+ Merge LR data and TB data.

```{r}
reg_data_10mi <- bind_rows(LR_10mi_y_owner, TB_10mi_y_well)
```


## CF Analysis

```{r, echo=F}
# /*===== control variables =====*/
# remove gdd_in
cov_ls <- c(
  # --- weather --- #
  "pr_in","pet_in",
  # --- soil --- #
  "silttotal_r", "claytotal_r", "slope_r", "ksat_r", "awc_r"
  )

data <- reg_data_10mi
Y <- data[, usage]
T <- data[, treat2]
X <- data[, ..cov_ls]
cl_var <- data[, county_year] %>% factor()
```

### 1st CF

```{r, echo=F}
#/*--------------------------------*/
#' ## 1st CF
#/*--------------------------------*/
set.seed(23456)

forest_W_cl <- regression_forest(
  X, T, 
  clusters = cl_var,
  num.trees = 4000)
W_hat <- predict(forest_W_cl)$predictions

forest_Y_cl <- regression_forest(
  X, Y, 
  clusters = cl_var,
  num.trees = 4000)
Y_hat <- predict(forest_Y_cl)$predictions

cf_raw_cl <- causal_forest(
  X=X,
  Y=Y,
  W=T, 
  Y.hat = Y_hat, 
  W.hat = W_hat,
  clusters = cl_var,
  tune.parameters = "all",
  num.trees = 4000
)

varimp = variable_importance(cf_raw_cl)
selected_vars = which(varimp > mean (varimp))
# selected_vars = which(varimp/mean(varimp) > 0.2)
se_cov <- data[,cov_ls[selected_vars], with=FALSE]

vis_cf_raw_cl <- gen_impact_viz(
  cf_res= cf_raw_cl,
  data_base=data,
  treat_var='treat2',
  var_ls= cov_ls,
  var_ls_int = cov_ls
)
vis_cf_raw_cl
```

### 2nd CF

```{r, echo=F}
#/*--------------------------------*/
#' ## 2nd CF
#/*--------------------------------*/
cf_res_cl <- causal_forest(
  X=se_cov,
  Y=Y,
  W=T, 
  Y.hat = Y_hat, 
  W.hat = W_hat,
  clusters = cl_var,
  # sample.fraction = 0.4,
  num.trees = 4000,
  tune.parameters = "all",
  # tune.parameters = c(""),
)

#/*--------------------------------*/
#' ## Visualization
#/*--------------------------------*/
vis_cf_res_cl <-
  gen_impact_viz(
  cf_res= cf_res_cl,
  data_base=data,
  treat_var='treat2',
  var_ls= cov_ls[selected_vars],
  var_ls_int = cov_ls[selected_vars]
)
vis_cf_res_cl
```

