---
title: "Report: Estimating the Impact of Groundwater Allocation Policies on Irrigation Behavior"
author: "Shunkei Kakimoto"
output:
  html_document:
    number_sections: yes
    theme: flatly
    toc_float: yes
    toc: yes
    toc_depth: 3
geometry: margin=1in
---

```{r setup, include=FALSE}
library(knitr)
library(here)
here::i_am("GitControlled/Codes/2_grf_cf_analysis.rmd")

opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  message = FALSE,
  warning = FALSE, 
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)

# /*===== Basic Packages  =====*/
# /*---- Data Wrangling ----*/
library(data.table)
library(tidyverse)
library(DescTools)
library(maps)

# /*---- Visualization ----*/
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(viridis)
library(grid)
library(gridExtra)
library(GGally)

# /*---- Model Summary ----*/
library(stats)
library(modelsummary)
library(flextable)
library(officer)
library(officedown)
library(gt)
```

```{r include=F}
library(here)
```

# Objective
+ Quantify the heterogeneous impact of groundwater allocation policy on farmers' irrigation activity in Nebraska, and reveal which factor is the main driver to cause such a heterogeneity.

<br>


# Data
We used well-level groundwater extraction data focusing on two Nebraska's Natural Resources Districts: Lower Republican (LR) and Tri-Basin(TB) during 2008-2015. Throughout the period, LR (treatment group) had an allocation of 9 acre-inches per year, while TB (control group) had no allocation. Furthermore, we used the wells located in a five-mile buffer from the border between LR and TB. 

```{r, echo=F}
# data_w_LR_TB <- 
#   here("Shared/Data/WaterAnalysis/data_w_LR_TB.rds") %>%
#   readRDS()

# nrd_bd <- here("Shared/Data/WaterAnalysis/NRD_bd/BND_NaturalResourceDistricts_DNR.shp") %>%
#   st_read() %>%
#   st_transform(., 4269) %>%
#   filter(NRD_Name %in% c("Tri-Basin", "Lower Republican"))

# well_sf <- data_w_LR_TB %>%
#   unique(.,by="wellid") %>%
#   .[,.(wellid, longdd, latdd)] %>%
#   # --- the geographic coordinate in the well data is NAD83 (espg=4269)--- #
#   st_as_sf(., coords = c("longdd","latdd"), crs = 4269)


 
# ggplot()+
#   geom_sf(data = nrd_bd, fill=NA, color="blue") +
#   geom_sf(data=well_sf, size=0.5) +
#   theme_void()
```


<br>

The variables we considered in the regression analysis are the following: <br />

+ **Weather variables**
  * From daily weather records of gridMET database, we obtained total precipitation (in mm) (`pr_in`) and total reference grass evaportranspiration (in mm) (`pet_in`) for the growing season (April to September). 

+ **Soil characteristics**
  * From the the Soil Survey Geographic (SSURGO) database, we collected the percentage of silt (`silttotal_r`), clay (`claytotal_r`), as well as hydraulic conductivity (in um/s, `ksat_r`), water holding capacity (in cm/cm. `awc_r`), and slope (in percentage, `slope_r`).




# Method
+ To estimate the treatment effect heterogeneity, we used Causal Forest (CF) model. CF is a machine learning methods developed specifically for identifying heterogeneous treatment effects (Athey and Imbens, 2016; Wager and Athey, 2018.) 

+ We employed cluster-robust estimation to take into account natural clusters in the data. Each cluster consists of time-series observations of the wells located within the same region.

+ To predict the heterogeneous treatment effects precisely, we built two separate CFs. The first CF was used to select the most important variables in a data-driven way among many variables. The variable of importance is determined by how how often each variable is used to split nodes, in other words how often a variable is judged as a factor affecting treatment effect heterogeneity. Utilizing those information, only important variables selected in the 1st CF were used to the second CF modeling. This enables second CF to detect treatment effect heterogeneity easily, especially in low-signal situations, and it is expected that CF can produce more precise predictions (Athey and Wager, 2019.)


# Results

```{r}
# === setup === #
library(here)
source(here("GitControlled/Codes/0_1_ls_packages.R"))
source(here("GitControlled/Codes/0_0_functions.R"))

# /*===== Data =====*/
reg_data <- 
  here("Shared/Data/WaterAnalysis/comp_reg_dt.rds") %>%
  readRDS() %>%
  .[year>=2008 & usage <= 40,]

agg_reg_data <-
  reg_data %>%
  .[year %in% 2008:2012] %>%
  .[,.(
    usage = sum(usage),
    treat2 = mean(treat2),
    # --- soil --- #
    silttotal_r = mean(silttotal_r),
    claytotal_r = mean(claytotal_r),
    slope_r = mean(slope_r),
    ksat_r = mean(ksat_r),
    awc_r = mean(awc_r),
    # --- weather --- #    
    pr_in = sum(pr_in),
    pet_in = sum(pet_in),
    gdd_in = sum(gdd_in),
    # --- tr --- #
    tr = tr
    ),by=wellid]

#/*--------------------------------*/
#' ## Preparation
#/*--------------------------------*/
# /*===== control variables =====*/
# remove gdd_in
cov_ls <- c(
  # --- weather --- #
  "pr_in","pet_in",
  # --- soil --- #
  "silttotal_r", "claytotal_r", "slope_r", "ksat_r", "awc_r"
  )

data <- reg_data
data <- agg_reg_data

# /*===== Training Dataset  =====*/
# --- dependent variable --- #
Y <- data[, usage]
# --- treatment indicator --- #
T <- data[, treat2]
# --- features --- #
X <- data[, ..cov_ls]

# --- cluster  --- #
# cl_var <- 
#   data.table::copy(data) %>%
#   .[,tr_year:=factor(paste0(tr,year))] %>%
#   .[,tr_year]

cl_var <- data[,tr] %>% as.factor()

#/*--------------------------------*/
#' ## 1st CF
#/*--------------------------------*/
set.seed(23456)

forest_W <- regression_forest(X, T, num.trees = 4000, clusters = cl_var)
W_hat <- predict(forest_W)$predictions

forest_Y <- regression_forest(X, Y, num.trees = 4000, clusters = cl_var)
Y_hat <- predict(forest_Y)$predictions

cf_raw <- causal_forest(
  X=X,
  Y=Y,
  W=T, 
  Y.hat = Y_hat, 
  W.hat = W_hat,
  clusters = cl_var,
  tune.parameters = "all",
  num.trees = 4000
)

varimp = variable_importance(cf_raw)
selected_vars = which(varimp > mean (varimp))
se_cov <- data[,cov_ls[selected_vars], with=FALSE]

#/*--------------------------------*/
#' ## 2nd CF
#/*--------------------------------*/
cf_res <- causal_forest(
  X=se_cov,
  Y=Y,
  W=T, 
  Y.hat = Y_hat, 
  W.hat = W_hat,
  clusters = cl_var,
  tune.parameters = "all",
  num.trees = 4000
)

#/*--------------------------------*/
#' ## Visualization
#/*--------------------------------*/
gen_impact_viz(
  cf_res= cf_res,
  data_base=data,
  treat_var='treat2',
  var_ls= cov_ls[selected_vars],
  var_ls_int = cov_ls[selected_vars]
)
```


+ The top row shows the histograms for each variable, and the bottom row shows the predicted treatment effects. Specifically, in each panel in the bottom row, the black line shows how the treatment effects varies, and the grey area indicates 95% CI for heterogeneous treatment effects.

+ As a results of the covariate selection process, `r cov_ls[selected_vars]` were selected. 

+ We found in-season total precipitation (`pr_in`) contributed strong heterogeneity in treatment effects. For regions where precipitation is low, farmers' groundwater use was more strongly regulated, and the effects of the regulation became less in the regions where precipitation is high.  

+ This finding suggests that it is preferable to account for the spatial gradients in precipitation in designing groundwater allocation policy to achieve higher economic efficiency. 





